Analyse gender in music psychology from journal publication data

### 2025-09-26 manuscript/manuscript.qmd
small tweaks in intro, much work on discussion.

abstract: "Academia suffers from various issues regarding equity. One aspect is gender inequality in academic authorship, where many studies show that women are often underrepresented. Due to authorship differences across disciplines, the goal of this study is to provide a current overview the gender distribution of authorship within music psychology. A total of 3,373 papers published between 2000 and 2025 across five core music psychology journals were analyzed with respect to author gender and authorship role (first, last, solo, coauthor). In addition, we explored gender patterns related to citations, open-access publishing, and keywords. Overall, female authors were in the minority, accounting for 40.2% of all authors. However, the distribution of authorship roles diverged notably from this overall proportion: women were more likely to be first authors (OR = 1.41), equally likely to be solo authors (odds ratio, OR = 1.11) or coauthors (OR = 1.00), but less likely to be last authors (OR = 0.73). These patterns have become more pronounced over the past 15 years. No substantial gender differences in citation counts were observed. Analyses of geographical variation revealed clear cross-country differences, potentially reflecting both the status of women and the historical development of the discipline in particular regions. Finally, an examination of keywords suggested broad thematic preferences differing by gender. Although this work overall shows that the field of music psychology is more balanced than some other (STEM) fields, it provides a picture that hopefully inspires discussions and initiatives to further promote fairness and equity in academia."

@@

Research across several scientific disciplines show that women tend to be less represented as authors compared to men [@banks2025women; @son2022scientific]. As the topics, approaches, and methods attract differential interest from men and women, it is important to recognise that fields of scholarship and academic disciplines vary considerably in terms of gender distribution [@huang2020]. For example, a large survey of authors by @gonzalez2020women showed that the hard sciences (N = 119,592) had the lowest prevalence of women (14.8%), whereas in the biological and social sciences (N = 262,122) the proportion was substantially higher (43.3%), but not equal. In psychology, which is perhaps the closest benchmark for the present focus on music psychology, female authors accounted for 45.2% of the sample (N = 90,067). Encouragingly, however, studies looking at various year ranges between 1960 until 2024 show a general trend that the ratio of women to men in authorships is improving [@gonzalez2020women; @ioannidis2023gender; @jemielniak2025gender; @sanchez2024analysis]. Yet, there is evidence that this improvement is plateauing [@jemielniak2025gender]. Further, although women are more likely to be first author, women are still generally unfairly underrepresented as the last author [@bruck2023bibliometric; @gonzalez2020women; @rock2021quantifying; @shah2021gender]. There could be several reasons for such a disparity: two key aspects that are typically explored in such **article analysis [TE: did you think citing specific studies here?]** papers: geographical locations and keyword/topics.

Past studies have explored the gender distribution could by due to geographical regions. For example, men out-numbered women more so in high-income compared to low-income countries [@ioannidis2023gender]. However, there are also some unexpected trends: while female representation is lowest in countries like Latin America, Caribbean [in physics journals, @son2022scientific] and in South Korea, Japan, and Austria [in medical journals, @bruck2023bibliometric], females were most highly represented in countries like India and Africa [@bruck2023bibliometric; @son2022scientific]. Human development indicators and gender inequality indicators have also revealed systematic inequalities in authorship. women’s academic success is correlated  positively with national indicators of gender equity [@chan2020]. However, this does not seem to be as clearly reflected in authorships. Female scientific output is lower in countries ranked in lowest quartile for human development and gender equity, female scientific output is also lower in countries very high in gender equality; better equality seemed to occur in high and medium-developed countries [@sugimoto2015relationship]. Another recent paper shows that female authorship rates are most balanced in countries with low to intermediate Human Development Index [@sanchez2024analysis]. Overall, while socioeconomic status of certain countries might be a reason for unbalanced female authorship [@ioannidis2023gender], human development might not fully explain such differences [@bruck2023bibliometric; @sanchez2024analysis; @son2022scientific], and further research is required to better understand the trends.

Another aspect that differs between distribution of gender in authorship is the research methodologies and topics. In terms of methodologies, women are are less likely to publish quantitative and experimental studies, but rather publish qualitative work [@ashmos2011gendering; @nunkoo2020three; @sebo2020gender; @thelwall2019gender; @zhang2023gender], perhaps as they demonstrate better relational skill involved in qualitative studies, like prolonged relationships and emotional ties with research participants [@sebo2020gender]. Interestingly, such stereotypes occur in the opposite direction: when assessing fictive research abstracts-one with quantitative and one with a qualitative design- scientific quality of the qualitative abstract was ranked more trustworthy and accurate when assigned to a female author [@johansson2002gender]. In an analyses of article keywords of medical journals, female-authored articles were more associated with keywords more related to healthcare-related themes like patient involvement, insurance, and quality-of-care compared to males [@bruck2023bibliometric]. Similarly, in computational linguistics, woman are more likely to publish on speech, social, and conversational topics than males; the latter are more likely to publish in formal mathematical, syntax, and semantic approaches [@vogel2012he]. These trends could be explained by the idea that female researchers often conduct research on societal progress, while males prefer research aimed at scientific progress [@zhang2021gender]. Overall, research shows that women choose qualitative research on social and societal topics, while males author papers using more quantitative methods on theoretical and analytical topics.

Looking more broadly past the information within papers themselves, other research provides some further explanations for discrepancies in female/male authorships. Despite efforts to give fair credit for author contributions [@ni2021gendered] using, for example, the Contributor Roles Taxonomy (CRediT) system, assigning authorship can be unclear. Women are more likely to experience authorship disagreements, for example, when to decide authorship: women prefer to discuss in earlier stages, while men choose authorship at the final stage [@ni2021gendered]. Another reason for the gender gap could also come from parenthood and parental leave, which account for about ~40% of gender gap in career advancement [@nielsen2024getting]. Additionally, women faculty perform more university, campus, and departmental services than men in general [@guarino2017faculty]. Fortunately, there are strides to improve the current situation, with opinion papers discussing way to improve receipt and reporting of intellectual credit [@banks2025women] as well as creating equitable environments in academic science [@martinez2024comparison]. To improve academic equity issues, it is worthwhile focusing on our discipline and to assess within subdisciplines to provide more 'localised' support to improve the equity in music psychology. Indeed, the past efforts such as @anglada2019visualizing have already provided a current overview the publications in the music psychology field with suggestions of future directions to improve the field. @eerola2023transparency showcases how Open Science practices (e.g., preregistrations, sharing research materials, data, and analysis scripts) are relatively limited, and encourage authors in the field to start implementing such practices. @jakubowski2024 explores participant samples and musical stimuli used across a wide range of experiment to give an idea of how limited or generalizable the field is. In a similar way to these papers, the current paper aims to give a current overview of gender patterns in authorship in the field of music psychology.

@@

Authorship is a crucial aspect in academia as a marker of scholarly success and strongly influences academic career progression, influencing recognition, funding, and advancement opportunities. However, there are several inequities within this aspect of academia, with women often being underrepresented in aspects such as authorships. The goal of the current paper was to provide a snapshot of authorship prevalence and roles across gender. While we recognise that gender is a complex and multidimensional social construct, and there are limitations to treating gender as a binary category, we used a binary male-female classification consistent with prior meta-science research on gender and authorship [@son2022scientific; @shah2021gender; @rock2021quantifying; @ni2021gendered; @gonzalez2020women; @wais2006]. As male-female authorship representations differ across different academic disciplines, it is worthwhile to diagnose the situation in music psychology.

In music psychology, the distribution of authors by gender remains unequal, with women representing 40.2% of authors. This proportion is higher than in musicology (34.8% @eerola2026inprep) and higher than in psychology more broadly, where women account for 33.2% of authors [@huang2020]. In terms of authorship roles, notable differences emerge. Women are relatively more likely than men to appear as first authors, a trend that has become characteristic of the field only in the past 15 years. This supports previous research showing that there is a positive trend with female representation increasing [@gonzalez2020women; @ioannidis2023gender; @jemielniak2025gender; @sanchez2024analysis]. In contrast, women remain underrepresented in the last authorship position, and this trend has not changed substantially over the last 15 years. This corresponds to the situation in other academic fields such as medicine [@bruck2023bibliometric; @shah2021gender], psychology [@gonzalez2020women], and biology [@rock2021quantifying]. Given that last authorship in the social sciences is not universally defined but is increasingly associated with seniority, supervisory responsibility, or principal investigator status [@drivas2024evolution], this underrepresentation suggests that women are less likely to occupy leadership roles such as lab heads or holders of substantial research resources. This pattern is consistent with broader evidence showing that women remain underrepresented in senior academic positions, including professorial appointments [@bakker2016tenure], invitations to contribute to journals, and authorship in high-prestige outlets [@holman2018gender]. Related analyses from science and medicine further show that women are more often associated with conducting experiments, whereas men are disproportionately represented in authorship roles linked to leadership and oversight [@macaluso2016science]. This suggests that the more 'leadership' author position is more likely to go to the male author.

@@

**->  (potential reasons: women faculty perform more university/campus/departmental services @guarino2017faculty )
[TE: is this supporting the idea that women are publishing more access than men? Or is this more about the lack of senior positions, which are probably not going to be achieved with internal service?]**

Turning to potential drivers of these gender differences, geographical and cultural factors appear to play a major role. Our summaries of gender patterns across continents and countries indicate clear cross-national variation. Large Commonwealth nations, namely Australia, Canada, and the United Kingdom, seem to provide a cultural climate more supportive of women in research, as reflected in the relatively high odds ratios of women appearing as authors (in any authorship position) in music psychology. This pattern, however, is not universal across all countries examined [@chan2020]. Prior work shows that women’s research success is positively correlated with national indicators of gender equity [@chan2020]. This is likely to be related to a career length, which strongly correlates with overall productivity. Women exhibit higher dropout rates than men, particularly during the 5–10 years following their first publication [@huang2020], but policies geared towards equity and support for career breaks and caring responsibilities may well contribute towards the observed country-specific differences. Nevertheless, prior analyses demonstrate that even when women constitute a smaller share of researchers within a discipline or country, their contributions are often more impactful than those of their male colleagues [@chan2020]. When examining countries where women have significantly lower odds of authorship compared to men (Japan, Belgium, Austria, Sweden, and Turkey), it is not straightforward to conclude that the lower proportion of female author is related gender equality rankings. The notable exception is Turkey, which is positioned lower according to the Gender Inequality Index [@UNDPHDR2024].

The keyword analysis of the articles indicated thematic differences in the topics studied by women and men. Research areas related to children, well-being, health, and mental health were more frequently associated with women. This pattern is consistent with observations in psychology more broadly, where women are more strongly represented in sub-disciplines that focus on (health)care and nurturing [@bruck2023bibliometric; @gonzalez2020women]. The higher likelihood of women studying topics related to singing may be connected to prevailing gender stereotypes, or to the early negative perceptions of singing among boys [@Warzecha2013] and men [@palkki2015gender]. In contrast, topics related to cognition and computation were more often associated with men, which reflects a wider trend in psychology [@gonzalez2020women]. In a similar trend in computational linguistics, woman are more likely to publish on speech, social and conversational topics than males, who are more likely to publish in formal mathematical, syntax, and semantic approaches [@vogel2012he]. It perhaps might be interesting to note that 'emotion' has an equal balance between men and women. **Although this may come as a surprise coming from different disciplines, music emotion can be a relatively 'analytical' aspect in music psychology, where emotion from music is attempted to be decoded in a more analytical way (top 3 authors for the keyword "emotion" are majority male, Saarikallio, Juslin, and Schubert, but "emotion regulation" top three is fully female), as well as being used in a more 'emotional' sense. This is the same for the keyword "expression". Although on first glance, it might fit the stereotype that this keyword might be more related to females, the "performance expression"  is again related to a more analytical coding aspect (Marc Leman, Laura Bishop, and Roger Chaffin as top 3 authors).**

In summary, music psychology has similar groupings of topic for female and male authors as in other disciplines of psychology and medicines. Below we also discuss how this information can help benefit the general field towards more equity with academia.

>>>>

abstract: "Academia suffers from various issues regarding equity. One such issue is gender inequality in authorship, where many studies show that women are often underrepresented. Due to authorship differences across disciplines, the goal of this study is to provide a current overview the gender distribution of authorship within music psychology. A total of 3,373 papers published between 2000 and 2025 across five core music psychology journals were analyzed with respect to author gender and authorship role (first, last, solo, and coauthor). In addition, we explored gender patterns related to citations, open-access publishing, and keywords. Overall, female authors were in the minority, accounting for 40.2% of all authors. However, the distribution of authorship roles diverged notably from this overall proportion: women were more likely to be first authors (OR = 1.41), equally likely to be solo authors (odds ratio, OR = 1.11) or coauthors (OR = 1.00), but less likely to be last authors (OR = 0.73). These patterns have become more pronounced over the past 15 years. No substantial gender differences in citation counts were observed. Analyses of geographical variation revealed clear country and continental differences, potentially reflecting both the status of women and the historical development of the discipline in particular regions. Finally, an examination of keywords suggested broad thematic preferences differing by gender. Although this work overall shows that the field of music psychology is more balanced than some other (STEM) fields, it provides a picture to inspire discussions and initiatives to further promote fairness and equity in academia."

@@

Research across several scientific disciplines show that women tend to be less represented as authors compared to men [@banks2025women; @son2022scientific]. As the topics, approaches, and methods attract differential interest from men and women, it is important to recognise that fields of scholarship and academic disciplines vary considerably in terms of gender distribution [@huang2020]. For example, a large survey of authors by @gonzalez2020women showed that the hard sciences (N = 119,592) had the lowest prevalence of women (14.8%), whereas in the biological and social sciences (N = 262,122) the proportion was substantially higher (43.3%), but not equal. In psychology, which is perhaps the closest benchmark for the present focus on music psychology, female authors accounted for 45.2% of the sample (N = 90,067). Encouragingly, however, studies looking at various year ranges between 1960 until 2024 show a general trend that the ratio of women to men in authorships is improving [@gonzalez2020women; @ioannidis2023gender; @jemielniak2025gender; @sanchez2024analysis]. Yet, there is evidence that this improvement is plateauing [@jemielniak2025gender]. Further, although women are more likely to be first author, women are still generally unfairly underrepresented as the last author [@bruck2023bibliometric; @gonzalez2020women; @rock2021quantifying; @shah2021gender].

Past studies have explored the gender distribution according to geographical regions and in relationship to country demographics. In one study, men out-numbered women more so in high-income compared to low-income countries [@ioannidis2023gender]. However, there are also some unexpected trends: while female representation is lowest in countries like Latin America, Caribbean [in physics journals, @son2022scientific] and in South Korea, Japan, and Austria [in medical journals, @bruck2023bibliometric], females were most highly represented in countries like India and Africa [@bruck2023bibliometric; @son2022scientific]. Human development indicators and gender inequality indicators have also revealed systematic inequalities in academia. However, while national indicators of gender equity is positively correlated with women’s academic success [@chan2020], this does not seem to be as clearly reflected in authorships. Female scientific output is not only lower in countries ranked in lowest quartile for human development and gender equity, but also in countries very high in gender equality; better equality seemed to occur in high and medium-developed countries [@sugimoto2015relationship]. Another recent paper shows that female authorship rates are most balanced in countries with low to intermediate Human Development Index [@sanchez2024analysis]. Overall, while socioeconomic status of certain countries might be a reason for unbalanced female authorship [@ioannidis2023gender], human development might not fully explain such differences [@bruck2023bibliometric; @sanchez2024analysis; @son2022scientific], and further research is required to better understand the trends.

Another aspect that differs between distribution of gender in authorship is the research methodologies and topics. In terms of methodologies, women are are less likely to publish quantitative and experimental studies, but rather publish qualitative work [@ashmos2011gendering; @nunkoo2020three; @sebo2020gender; @thelwall2019gender; @zhang2023gender], perhaps as they demonstrate better relational skill involved in qualitative studies, like prolonged relationships and emotional ties with research participants [@sebo2020gender]. Interestingly, such stereotypes occur in the opposite direction: when assessing fictive research abstracts-one with quantitative and one with a qualitative design- scientific quality of the qualitative abstract was ranked more trustworthy and accurate when assigned to a female author [@johansson2002gender]. There are also key different when assessing article keywords. In one analysis of article keywords of medical journals, female-authored articles were more associated with keywords more related to healthcare-related themes like patient involvement, insurance, and quality-of-care compared to males [@bruck2023bibliometric]. Similarly, in computational linguistics, woman are more likely to publish on speech, social, and conversational topics than males; the latter are more likely to publish in formal mathematical, syntax, and semantic approaches [@vogel2012he]. These trends could be explained by the idea that female researchers often conduct research on societal progress, while males prefer research aimed at scientific progress [@zhang2021gender]. Overall, research shows that women choose qualitative research on social and societal topics, while males author papers using more quantitative methods on theoretical and analytical topics.

Looking more broadly past the information within papers themselves, other research provides some further explanations for discrepancies in female/male authorships. Despite efforts to give fair credit for author contributions [@ni2021gendered] using, for example, the Contributor Roles Taxonomy (CRediT) system, assigning authorship can be unclear. Women are more likely to experience authorship disagreements, for example, when to decide authorship: women prefer to discuss in earlier stages, while men choose authorship at the final stage [@ni2021gendered]. Another reason for the gender gap could also come from parenthood and parental leave, which account for about ~40% of gender gap in career advancement [@nielsen2024getting]. Additionally, women faculty perform more university, campus, and departmental services than men in general [@guarino2017faculty]. Fortunately, there are strides to improve the current situation, with opinion papers discussing way to improve receipt and reporting of intellectual credit [@banks2025women] as well as creating equitable environments in academic science [@martinez2024comparison]. To improve academic equity issues, it is worthwhile focusing on subdiscipline to provide more 'localised' support to improve the equity in field. This was the aim of the current paper to look within our own field of music psychology. Indeed, the past efforts such as @anglada2019visualizing have already provided a current overview the publications in the music psychology field with suggestions of future directions to improve the field. @eerola2023transparency showcases how Open Science practices (e.g., preregistrations, sharing research materials, data, and analysis scripts) are relatively limited, and encourage authors in the field to start implementing such practices. @jakubowski2024 explores participant samples and musical stimuli used across a wide range of experiment to give an idea of how limited or generalizable the field is. In a similar way to these papers, the current paper aims to give a current overview of gender patterns in authorship in the field of music psychology.

@@

Authorship is a crucial marker of scholarly success in academia, which strongly influences academic career progression, recognition, funding, and advancement opportunities. However, there are several inequities within academic authorship, with women often being underrepresented. As male-female authorship representations differ across different academic disciplines, it is worthwhile diagnosing the situation in the field of music psychology. The goal of the current paper was to provide a snapshot of authorship prevalence and roles across gender in core music psychology journals, specifically Musicae Scientiae, Psychology of Music, Music Perception, Journal of New Music Research, and Music & Science. Overall, we found that the distribution of authors by gender remains unequal, with women representing 40.2% of authors. This proportion is higher than in musicology (34.8% @eerola2026inprep) and higher than in psychology more broadly, where women account for a third of authors (33.2% [@huang2020]; 36.2% [@gonzalez2020women]). This representation is also much higher than in other STEM subjects of math, physics and computer (15% [@huang2020]) and physics topics like astronomy and bioscience (17.8%, @son2022scientific). While our current findings suggests that the field of music psychology is doing better in fostering gender equity than certain other fields, women are still overall underrepresented. In exploring the nuances behind this, we further analysed differences between authorship role, number of citations, geography, and article keywords.

In terms of authorship roles, notable differences emerge. Women are more likely than men to appear as first authors, a trend that has become characteristic of the field only in the past 15 years. This supports previous research showing that there is a positive trend with female representation increasing [@gonzalez2020women; @ioannidis2023gender; @jemielniak2025gender; @sanchez2024analysis]. In contrast, women remain underrepresented in the last authorship position, and this trend has not changed substantially over the last 15 years. This underrepresentation in woman as last authors corresponds to the situation in other academic fields such as medicine [@bruck2023bibliometric; @shah2021gender], psychology [@gonzalez2020women], and biology [@rock2021quantifying]. Although last authorship in the social sciences is not necessarily universally defined, it is nonetheless increasingly associated with seniority, supervisory responsibility, or principal investigator status [@drivas2024evolution]. Therefore, this underrepresentation suggests that women are less likely to occupy leadership roles such as lab heads or holders of substantial research resources. This pattern is consistent with broader evidence showing that women remain underrepresented in senior academic positions, including professorial appointments [@bakker2016tenure], invitations to contribute to journals, and authorship in high-prestige outlets [@holman2018gender]. Related analyses from science and medicine further show that women are more often associated with conducting experiments, whereas men are disproportionately represented in authorship roles linked to leadership and oversight [@macaluso2016science]. This patterns is also consistent with the idea of a "leaky pipeline", where women are more likely to drop away from academic careers with increasing seniority, especially between doctoral and (consolidated) researcher positions [@gonzalez2020women] and generally have shorter academic careers [@sanchez2024analysis]. On a broader level, this might highlight the need for more mentorship programs for (junior) women to senior positions. Indeed, mentorship programs have been shown support remaining in academia [@gardiner2007show]. We note that within the broader music psychology community, there are some mentorship programs in place, for example, Women in Music Information Retrieval WIMIR (https://wimir.wordpress.com/) and the Society for Music Perception and Cognition has resources for trainees and a Mentorship committe (https://www.musicperception.org/committees) and often holds mentor-mentee meetings at conferences. Although these measures have been in places for some years, it might still take some time for the effect to translate and additional mentorship programs could be welcome.

@@

Turning to potential drivers of these gender differences, geographical and cultural factors appear to play a major role. Our summaries of gender patterns across continents and countries indicate clear cross-national variation, supporting the idea that certain inequity may stem from national cultural factors [@bruck2023bibliometric]. Large Commonwealth nations, namely Australia, Canada, and the United Kingdom, seem to provide a cultural climate more supportive of women in research, as reflected in the relatively high odds ratios of women appearing as authors (in any authorship position) in music psychology. This pattern, however, is not universal across all countries examined [@chan2020]. Prior work shows that women’s research success can be positively correlated with national indicators of gender equity [@chan2020] or are related to countries with intermediate Human Development Index [@sanchez2024analysis; @sugimoto2015relationship]. This discrepancy between author representation could likely to be related to a career length, which strongly correlates with overall productivity. Women exhibit higher dropout rates than men, particularly during the 5–10 years following their first publication [@huang2020], but policies geared towards equity and support for career breaks and caring responsibilities may well contribute towards the observed country-specific differences. Nevertheless, prior analyses demonstrate that even when women constitute a smaller share of researchers within a discipline or country, their contributions are often more impactful than those of their male colleagues [@chan2020]. When examining countries where women have significantly lower odds of authorship compared to men (Japan, Belgium, Austria, Sweden, and Turkey), it is not straightforward to conclude that the lower proportion of female author is related gender equality rankings. The notable exception is Turkey, which is positioned lower according to the Gender Inequality Index [@UNDPHDR2024].

The keyword analysis of the articles indicated thematic differences in the topics studied by women and men. Research areas related to children, well-being, health, and mental health were more frequently associated with women. This pattern is consistent with observations in psychology more broadly, where women are more strongly represented in sub-disciplines that focus on (health)care and nurturing [@bruck2023bibliometric; @gonzalez2020women]. The higher likelihood of women studying topics related to singing may be connected to prevailing gender stereotypes, or to the early negative perceptions of singing among boys [@Warzecha2013] and men [@palkki2015gender]. In contrast, topics related to cognition and computation were more often associated with men, which reflects a wider trend in psychology [@gonzalez2020women]. In a similar trend in computational linguistics, woman are more likely to publish on speech, social and conversational topics than males, who are more likely to publish in formal mathematical, syntax, and semantic approaches [@vogel2012he]. It perhaps might be interesting to note that 'emotion' has an equal balance between men and women. **Although this may come as a surprise coming from different disciplines, music emotion can be a relatively 'analytical' aspect in music psychology, where emotion from music is attempted to be decoded in a more analytical way (top 3 authors for the keyword "emotion" are majority male, Saarikallio, Juslin, and Schubert, but "emotion regulation" top three is fully female), as well as being used in a more 'emotional' sense. This is the same for the keyword "expression". Although on first glance, it might fit the stereotype that this keyword might be more related to females, the "performance expression" is again related to a more analytical coding aspect (Marc Leman, Laura Bishop, and Roger Chaffin as top 3 authors).**  The difference that female prefer 'caring' topics over male authors fits with the general idea that female researchers value research on societal progress, while males prefer research aimed at scientific progress [@zhang2021gender]. This fits with another potential explanation for the disparity between authorship, namely that women might also lean toward and execute more university/campus/departmental services than men [@guarino2017faculty]. Over time, performing such services to universities are time away from other work on acquiring funding and leading research, which would aggregate over time to time away from publishing research. It is nonetheless important for such services are completed; in some cases it could be there is more encouragement for males to take on these kinds of roles, but also it could be that success in academia could also be more societal defined as not only publications [@kiai2019protect], but as a whole should celebrate achievements that support internal, local and community services in a broader sense.

There are certain limitations of the current research. The gender of the authors are not part of the database - gender was inferred based on author name using _genderize API_ [@wais2006]. Nonetheless, we maintain that the conclusions may still hold. First, both authors checked whether any of the gender attribution of major names needed fixing (see accompanying code). Second, there error (confidence) of the gender attribution was relatively small (only `89` had low (< 0.55) attribution probability, while 89.3% had high (> 0.90) attribution probability), so it is unlikely that the remaining names would significantly change the main conclusions. Another limitation is treating gender as a binary category. While we recognise that gender is a complex and multidimensional social construct, we used a binary male-female classification consistent with prior meta-science research on gender and authorship [@son2022scientific; @shah2021gender; @rock2021quantifying; @ni2021gendered; @gonzalez2020women; @wais2006] and because generally the number of non-binary authors is currently relatively low (0.8% @son2022scientific). Nonetheless, future research should also move towards using more inclusive, non-binary information. However, the main limitation is that such research indicates the symptoms of certain issues in academia, but not necessarily the causes. While we speculate on certain reasons for the current state of affairs, other kinds of research such as qualitative and longitudinal research would further elucidate the key problems, and where areas for improvements could be made to promite better equity in academia.
